---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SAvalidation

<!-- badges: start -->
<!-- badges: end -->

SAvalidation provides simple functions for running validation checks on seasonally adjusted time series and generating dashboards for further analysis of validation checks. 

## Installation

You can install the development version of SAvalidation like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example1}
library(SAvalidation)

level1_validation(data_to_check$nsa,data_to_check$sa)
```
A level 2 validation report can be created with `level2_validation()` which returns an html dashboard either in current working directory or a user specified directory

```{r,eval=FALSE}

level2_validation(data_to_check$nsa,data_to_check$sa,data_to_check$name)

```

Can also create plots from level 2 validation code for example the NSA against the SA

```{r }
nsa_sa_plot(data_to_check$nsa,data_to_check$sa)
```

Or the derived adjustment factor plot
```{r }
adjust_fact_plot(data_to_check$nsa,data_to_check$sa)
```
