---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SAvalidation

<!-- badges: start -->
<!-- badges: end -->

SAvalidation provides simple functions for running validation checks on seasonally adjusted time series and generating dashboards for further analysis of validation checks. 

## Installation

You can install the development version of SAvalidation like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SAvalidation)
## basic example code

level1_validation(data_to_check$nsa,data_to_check$sa)
```


Create a plot from level 2 validation code
```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
