---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SAvalidation

<!-- badges: start -->
<!-- badges: end -->

SAvalidation provides simple functions for running validation checks on seasonally adjusted time series and generating dashboards for further analysis of validation checks. 

## Installation

You can install the development version of SAvalidation like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SAvalidation)

data("data_to_check")

level1_validation(data_to_check$nsa,data_to_check$sa)
```


Create a plot from level 2 validation code for example the NSA against the SA

```{r }
nsa_sa_plot(data_to_check$nsa,data_to_check$sa)
```

<!-- Or the derived adjustment factor plot -->
<!-- ```{r } -->
<!-- adjust_fact_plot(data_to_check$nsa,data_to_check$sa) -->
<!-- ``` -->
